### 2023-04-21 paper.tex
two minor changes

April 2023
\vspace{5.5ex}

@@

From this, we calculate Welch's t statistic as usual:
$$ t_I = \frac{\mu^\text{A}_I - \mu^\text{B}_I}{\sqrt{v^\text{A}_I/|C_A| + v^\text{B}_I/|C_B|}}.$$

>>>>

April 2023
\vspace{4.5ex}

@@

From this, we calculate Welch's t statistic as usual:
$$ t_I = \frac{\mu^\text{A}_I - \mu^\text{B}_I}{\sqrt{\frac{v^\text{A}_I}{|C_A|} + \frac{v^\text{B}_I}{|C_B|}}}.$$
